\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-14 manuscript.Rmd
Added ffiliations

---
title             : "_Light Exposure Behavior Assessment (LEBA)_: Develop of a novel instrument to capture light exposure-related behaviours"
shorttitle        : "LEBA"

>>>>

---
title             : "_Light Exposure Behavior Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
shorttitle        : "LEBA"
